\bf Visual diagnostics for constrained optimisation with application to guided tours

### 2020-11-19 paper/paper.tex
added a hand-sketch on plots

{\centering \includegraphics[width=0.6\linewidth,height=0.3\textheight]{/Users/pmen0008/Desktop/paper-tour-vis/img/tour_path}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/toy-search-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/toy-interp-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/toy-pca-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/toy-pca-animated-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/toy-tour-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/interruption-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/polish-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/noisy-better-geo-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/kol-better-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/kol-random-1}

@@

{\centering \includegraphics{/Users/pmen0008/Desktop/paper-tour-vis/figs/kol-random-tuned-1}

>>>>

{\centering \includegraphics[width=0.6\linewidth,height=0.3\textheight]{/Users/dicook/students_PhD/Sherry/paper-tour-vis/img/tour_path}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/toy-search-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/toy-interp-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/toy-pca-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/toy-pca-animated-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/toy-tour-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/interruption-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/polish-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/noisy-better-geo-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/kol-better-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/kol-random-1}

@@

{\centering \includegraphics{/Users/dicook/students_PhD/Sherry/paper-tour-vis/figs/kol-random-tuned-1}
